\documentclass[a4paper,twocolumn,10pt]{article}
\input{preamble}

\title{Selected Notes on Infinite Series}
\author{Christian Stigen Larsen}
\date{May 2017}

\begin{document}
  \maketitle
  \section*{Geometric series}
  $\sum_{n=0}^{\infty} a_n$ where $|a_{n+1} = ra_n$ for all $n \geq 0$ is
  called a \textit{geometric series}, i.e.~each term is a multiple $r$ of the
  previous.

  \paragraph{Theorem} If $|r| < 1$, then the series converges with the sum
  $\frac{a_0}{1-r}$. If $|r| \geq 1$, it diverges.

  \paragraph{Theorem} If $\lim_{n\to\infty}{a_n}\neq 0$ or the limit does not
  exist, then $\sum a_n$ diverges.

  \paragraph{Theorem} The harmonic series $\sum \frac{1}{n}$ diverges.

  \section*{The integral test}

  \paragraph{Theorem} If $f(n) = a_n$ for all $n$, then $\sum a_n$ and $\int
  f(x) \diff x$ either both converge or diverge.

  \section*{The comparison test}
  Suppose $\sum a_n$ and $\sum b_n$ are positive-term series. Then
  \begin{enumerate}
    \item $\sum a_n$ converges if $\sum b_n$ converges \textit{and} $a_n \leq
      b_n$ for all $n$.
    \item $\sum a_n$ diverges if $\sum b_n$ diverges \textit{and} $a_n \geq
      b_n$ for all $n$.
  \end{enumerate}

  \section*{The limit comparison test}
  Suppose $\sum a_n$ and $\sum b_n$ are positive-term series. If $L =
  \lim_{n\to\infty}{\frac{a_n}{b_n}}$ exists and $0<L<+\infty$, then either
  \textit{both converge} or \textit{both diverge}.

  \section*{Alternating series}
  \paragraph{Theorem}
  If $a_n > a_{n+1} > 0$ for all $n$ and $\lim_{n\to\infty}{a_n} = 0$, then the
  alternating series $\sum_{n=1}^{\infty} (-1)^{n+1} a_n$ converges.

  \paragraph{Theorem}
  If the series $\sum|a_n|$ converges (\textit{absolute convergence}), then so
  does the series $\sum a_n$.

  \section*{The ratio test}
  \paragraph{Theorem} If $\rho = \lim_{n\to\infty}|\frac{a_{n+1}}{a_n}|$ exists
  or is infinite, then the $\sum a_n$ of non-zero terms \textit{converges
  absolutely} if $\rho < 1$, diverges if $\rho > 1$ and is inconclusive if
  $\rho = 1$.

  \section*{The root test}
  If $\rho = \lim_{n\to\infty}{\sqrt[n]{|a_n|}}$ exists or is infinite, then the
  infinite series $\sum a_n$ \textit{converges absolutely} if $\rho < 1$,
  diverges if $\rho > 1$. The test is inconclusive for $\rho = 1$.

  \section*{Power series}
  \paragraph{Theorem} If $\sum a_n x^n$ is a power series, then either
  \begin{enumerate}
    \item The series converges absolutely for all $x$, or
    \item The series converges only when $x=0$, or
    \item There exists a number $R>0$ (\textit{radius of convergence}) such
      that $\sum a_n x^n$ converges absolutely if $|x| < R$ and diverges if
      $|x| > R$.
  \end{enumerate}
  After finding the open interval $\left< x_0-R, x_0+R \right>$, make sure to
  test each end point for convergence or divergence.

\end{document}
